---
title: "jt3174_HW2"
author: "Jingyi Tang"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}

set.seed(1)
knitr::opts_chunk$set(echo = TRUE)

# load library
library(tidyverse)

#set workding directory
setwd("/Users/jt/Downloads/Columbia_University/P8157_Longitudinal/LDA_HW2")
getwd()

```

# Tidy Data

```{r}

# Short cut for insert code chuck: Cmd + option + i
# relative path for mac: use . for relative path

#################################################################

# read txt file, tab-delimited, skin.txt
skin = read.table("./data/skin.txt", skip = 1)

# short preview of skin to make sure that we are on the right track
head(skin)

# assign names to each variables
colnames(skin) = c("id", "center", "age", "skin", "gender", "exposure", "y", "treatment", "year")

# check the data tidied
head(skin)

#################################################################

# read txt file, space-delimited, toenail.txt
toenail = read.table("./data/toenail.txt", skip = 1)

# check
head(toenail)

# assign column names
colnames(toenail) = c("id", "response", "treatment", "month", "visit")

# check
head(toenail)

```

Data tidy is finished.

# Question 1

In a randomized, double-blind, __parallel-group__, multicenter study comparing __two oral treatments (denoted A and B)__ for toe-nail infection (De Backer etal., 1998; also see Lesaffre and Spiessons, 2001), patients were evaluated for __the degree of onycholysis__ (the degree of separation of the nail plate from the nail-bed) at __baseline (week 0) and at weeks 4, 8, 12, 24, 36, and 48 thereafter__. The onycholysis outcome variable is __binary__ (none or mild versus moderate or severe). The binary outcome was evaluated on __294 patients__ comprising a total of __1908 measurements__. The main objective of the analyses is to *__compare the effects of oral treatments A and B__* on *__changes in the probability of the binary onycholysis outcome__* over the duration of the study. The raw data are stored in an external file: toenail.dat. Each row of the data set contains the following five variables: ID, Y, Treatment, Month, Visit. The binary onycholysis __outcome variable Y__ is _coded 0 = none or mild, 1 = moderate or severe_. The categorical variable __Treatment__ is _coded 1 = oral treatment A, 0 = oral treatment B_.
The variable Month denotes the exact timing of measurements in months. The variable Visit denotes the visit number (visit numbers 1-7 correspond to scheduled visits at 0, 4, 8, 12, 24, 36, and 48 weeks).

## Question 1 - Part 1

